Comments on the revised version

### 2018-03-02 paper/paper.tex

The best values are outlined in bold in the table. These values give the best
attainable performance in the search set defined in~\ref{subsec:policies}.
Note that there seems to be some regularity; for instance the SAF policy is remarkably
inefficient and the LQF policy works very well. However there are traces for which LQF is not optimal. Moreover, these
are~\textit{a-posteriori} results, which means that we only know
\textit{post-factum} that this policy would have been better.

>>>>

The best values are outlined in bold in the table. These values give the best
attainable performance in the search set defined in~\ref{subsec:policies}.
Note that there seems to be some regularity; for instance the SAF policy is
remarkably inefficient and the LQF policy works very well. However there are
traces for which LQF is not optimal.  For these machines, ordering jobs by
decreasing size seems to be more efficient than ordering them by time. This
study is limited in scope, and these results are possibly different on other
machines. Moreover, the simulator model is simplistic and the relative order of
policies may change, for instance when introducing a topology model in the
simulations. This is however sufficient to study adaptive policies.

These are~\textit{a-posteriori} results, which means that we only know
\textit{post-factum} that this policy would have been better.

### 2018-03-02 paper/revision.tex

You are right, we clarified this point in the text (SECTION xx - PAGE xx).\\

@@

Doing this would drown the point in the author's opinion. 
QUE VEUX-TU DIRE VRAIMENT ICI?
Good remark, we agree it is an interesting point, which was addressed in our previous publication 'Tuning
Backfilling Queues' (JSSPP17).
\medskip

@@

(2) Second, we used a light simulation model. In this model, we do make
machines *more* similar to each other by neglecting topological differences. It
can be reasonably expected that differences between systems should *increase*
rather than decrease, when moving away from a simplistic model to the real
systems.
We modified the present experiments to use leave-one-out cross
validation in the hyperparameter selection, and we clarified the reasons for
chosing this experimental protocol.
We are preparing a subsequent study using an approach closer to what you
describe, in which we greatly increase the number of workload logs used.
\medskip

@@

Right, a justification was clearly missing, this value is taken as to be
sufficiently larger than the values previously reported, see e.g. "Batsim: a
Realistic Language-Independent Resources and Jobs Management Systems Simulator"
which reports few percents of variation of the simulated metric compared to the
metric on the real systems. We added this remark in the text.\\

>>>>

You are right, we clarified this point in the text (Section 6.6.1 - Page 7).\\

@@

It is an interesting point, which was addressed in our previous publication
'Tuning Backfilling Queues' (JSSPP17). Here, we prefer to be cautious. Indeed,
the high number of simulations in this work forced us to use a simplistic
simulator model. We can reasonably expect these results to change when adding
a topology model, or a model of job interference for example. While we believe
this simple model is sufficient to study the behavior of adaptive policies, we
prefer not to draw conclusions about the systems themselves from these
simulations. We added this remark in the text (Section 6.3.1 - page 10).

\medskip

@@

(2) Second, we need to run high number of simulations, and accordingly we used a light simulation model . In this model, we do make
machines *more* similar to each other by neglecting topological differences. It
can be reasonably expected that differences between systems should *increase*
rather than decrease, when moving away from a simplistic model to the real
systems. This reason is also why we don't expand on which fixed strategy is 
the best. Indeed, the results are probably different when adding a topology model,
job interference, or an I/O congestion model. We do believe this simple
model is enough for studying adaptive policies though. We added a remark in 
the text (Section 6.3.1 - Page 10)

We modified the present experiments to use leave-one-out cross
validation in the hyperparameter selection, and we clarified the reasons for
chosing this experimental protocol.
We are preparing a subsequent study using an approach closer to what you
describe, in which we greatly increase the number of workload logs used.
\medskip

@@

Right, a justification was clearly missing, this value is taken as to be
sufficiently larger than the values previously reported, see e.g. "Batsim: a
Realistic Language-Independent Resources and Jobs Management Systems Simulator"
which reports few percents of variation of the simulated metric compared to the
metric on the real systems. We added this remark in the text (Section 5.2- Page 6).\\
